Decomposing biodiversity change to processes of extinction, colonization, and persistence across scales

### 2023-06-30 scripts/ms_scaling_changes.qmd
anonymizing repo

---
title: "Decomposing biodiversity change to processes of extinction, colonization, and persistence across scales"
author: "François Leroy et al."
format: 
  html:
    toc: true
    toc_float: true
    chunks:
    warning: false
    message: false
editor: visual
---

@@

The data used (*i.e.* CzAtlas and CzBBS) are not open thus we provide them already processed into species richness, colonization, extinction... per unit of area. If you are interested in accessing the raw datasets (with species identities), feel free to contact the following email address: leroy\@fzp.czu.cz.

>>>>

---
title: "Decomposing biodiversity change to processes of extinction, colonization, and persistence across scales"
format: 
  html:
    toc: true
    toc_float: true
    chunks:
    warning: false
    message: false
editor: visual
---

@@

The data used (*i.e.* CzAtlas and CzBBS) are not open thus we provide them already processed into species richness, colonization, extinction... per unit of area. If you are interested in accessing the raw datasets (with species identities), feel free to contact the corresponding author.
